A Roadmap for\\HEP Software and Computing R\&D\\for the 2020s

### 2018-06-20 CWP/papers/HSF-CWP-2017-01_roadmap/latex/authors.tex
Add Andronico as author and regenerated authors latex
* Add Giuseppe Andronico as authoe

Address taken from recent CMS publication, but not yet sure if the
University should be mentioned or not

* Add regenerated authors LaTeX file for arXiv

Albrecht, Johannes$^{68}$;
Alves Jr, Antonio Augusto$^{80}$;

@@

Anh-Ky, Nguyen$^{121}$;
Aphecetche, Laurent$^{65}$;

@@

Asai, Makoto$^{62,p}$;

@@

Bagliesi, Giuseppe$^{31}$;

@@

Bauerdick, Lothar A. T.$^{16,c}$;
Belforte, Stefano$^{34}$;
Benjamin, Douglas$^{81}$;
Bernius, Catrin$^{62}$;
Bhimji, Wahid$^{45}$;
Bianchi, Riccardo Maria$^{104}$;

@@

Biscarat, Catherine$^{51}$;

@@

Bloom, Kenneth$^{96}$;
Boccali, Tommaso$^{31}$;
Bockelman, Brian$^{96}$;
Bold, Tomasz$^{42}$;

@@

Boveia, Antonio$^{100}$;
Bozzi, Concezio$^{27}$;
Bracko, Marko$^{92,40}$;
Britton, David$^{85}$;
Buckley, Andy$^{85}$;

@@

Calafiura, Paolo$^{45}$;

@@

Carlino, Gianpaolo$^{30}$;
Castro, Nuno$^{46,95,d}$;

@@

Chang, Philip$^{74}$;
Chapman, John$^{75}$;

@@

Clarke, Peter$^{82}$;

@@

Cogneras, Eric$^{49}$;
Coles, Jeremy$^{75}$;
Collier, Ian$^{60}$;

@@

Costanzo, Davide$^{111}$;

@@

Cranmer, Kyle$^{56}$;

@@

Crooks, David$^{85}$;
Crépé-Renaudin, Sabine$^{51}$;
Currie, Robert$^{82}$;

@@

De, Kaushik$^{113}$;
De Cian, Michel$^{86}$;

@@

Derue, Frédéric$^{50}$;

@@

Di Guida, Salvatore$^{29}$;

@@

Doglioni, Caterina$^{90,h}$;
Dotti, Andrea$^{62,p}$;

@@

Duflot, Laurent$^{44}$;

@@

Egede, Ulrik$^{37}$;
Elmer, Peter$^{105,a}$;

@@

Farrell, Steven$^{45}$;
Ferber, Torben$^{72}$;
Filipcic, Andrej$^{40}$;
Fisk, Ian$^{63}$;

@@

Flix, José$^{58,7,g}$;
Formica, Andrea$^{38}$;
Forti, Alessandra$^{91}$;

@@

Frost, James$^{103}$;

@@

Gardner, Robert$^{79}$;
Garonne, Vincent$^{101}$;

@@

George, Simon$^{61}$;
Geurts, Frank$^{106}$;

@@

Giagu, Stefano$^{108,33}$;
Giffels, Manuel$^{41}$;
Gingrich, Douglas$^{69}$;

@@

Gligorov, Vladimir V.$^{50,b}$;
Glushkov, Ivan$^{113}$;
Gohn, Wesley$^{87}$;

@@

González Caballero, Isidro$^{102}$;
González Fernández, Juan R.$^{102}$;

@@

Grasland, Hadrien$^{44}$;
Gray, Heather$^{45}$;
Grillo, Lucia$^{91}$;
Guan, Wen$^{118}$;

@@

Gyurjyan, Vardan$^{39}$;
Hanushevsky, Andrew$^{62,p}$;

@@

Hauth, Thomas$^{41}$;

@@

Heinrich, Lukas$^{56}$;
Heiss, Andreas$^{41}$;

@@

Hildreth, Michael$^{98,f}$;
Hodgkinson, Mark$^{111}$;
Hoeche, Stefan$^{62,p}$;

@@

Huang, Xingtao$^{110}$;
Ivanchenko, Vladimir N.$^{5,114}$;
Ivanov, Todor$^{112}$;

@@

Jashal, Brij$^{67}$;

@@

Jones, Roger$^{88,a}$;
Jouvin, Michel$^{44,a}$;

@@

Kagan, Michael$^{62,p}$;
Kalderon, Charles William$^{90}$;
Kane, Meghan$^{64}$;

@@

Katz, Daniel S.$^{78}$;

@@

Kersevan, Borut Paul$^{89}$;

@@

Klute, Markus$^{93}$;
Komarov, Ilya$^{34,n}$;
Konstantinov, Dmitri$^{59}$;
Koppenburg, Patrick$^{55}$;

@@

Kreczko, Luke$^{71}$;
Kuhr, Thomas$^{48,a}$;

@@

Lampl, Walter$^{70}$;

@@

Lange, David$^{105,a}$;

@@

Leggett, Charles$^{45}$;
Letts, James$^{74}$;

@@

Li, Teng$^{82}$;

@@

Linacre, Jacob$^{60,m}$;

@@

Love, Peter$^{88}$;

@@

Magini, Nicolò$^{28}$;
Marshall, Zachary L$^{45}$;

@@

Martin-Haugh, Stewart$^{60}$;

@@

Mazumdar, Kajari$^{67}$;
McCauley, Thomas$^{98}$;

@@

McKee, Shawn$^{94,l}$;
McNab, Andrew$^{91}$;
Mehdiyev, Rashid$^{77}$;

@@

Menasce, Dario$^{29,a}$;

@@

Mete, Alaettin Serhan$^{73}$;
Michelotto, Michele$^{32}$;
Mitrevski, Jovan$^{48}$;

@@

Morgan, Ben$^{117}$;
Mount, Richard$^{62,p}$;
Moyse, Edward$^{93}$;
Murray, Sean$^{76,10}$;

@@

Neubauer, Mark S$^{78,a,k}$;

@@

Novaes, Sérgio$^{107}$;

@@

Ozturk, Nurcan$^{113}$;
Pacheco Pages, Andres$^{58,20,j}$;
Paganini, Michela$^{119}$;
Pansanel, Jerome$^{36}$;
Pascuzzi, Vincent R.$^{115}$;
Patrick, Glenn$^{60}$;

@@

Pearson, Ben$^{53}$;

@@

Perez-Calero Yzquierdo, Antonio$^{58,7,g}$;

@@

Petersen, Troels$^{54}$;

@@

Petzold, Andreas$^{41}$;

@@

Piilonen, Leo$^{122,i}$;

@@

Pivarski, Jim$^{105}$;

@@

Polci, Francesco$^{50}$;

@@

Puig Navarro, Albert$^{120}$;
Quast, Günter$^{41}$;
Raven, Gerhard$^{55,123}$;

@@

Ritter, Martin$^{48}$;

@@

Rodrigues, Eduardo$^{80,a,e}$;

@@

Rousseau, David$^{44}$;
Roy, Gareth$^{85}$;
Rybkine, Grigori$^{44}$;

@@

Sakuma, Tai$^{71}$;

@@

Sartirana, Andrea$^{47}$;
Schellman, Heidi$^{57}$;

@@

Schramm, Steven$^{84}$;

@@

Seidel, Sally$^{97}$;
Sekmen, Sezen$^{43}$;
Serfon, Cedric$^{101}$;
Severini, Horst$^{99}$;

@@

Seymour, Michael$^{91}$;

@@

Shapoval, Illya$^{45}$;

@@

Shiu, Jing-Ge$^{66}$;

@@

Skipsey, Sam$^{85}$;

@@

Sokoloff, Michael D$^{80,a}$;

@@

Stark, Giordon$^{79}$;
Stewart, Gordon$^{85}$;
Stewart, Graeme$^{5,a}$;
Sánchez, Arturo$^{116,19}$;

@@

Taffard, Anyes$^{73}$;
Tamponi, Umberto$^{35}$;
Templon, Jeff$^{55}$;

@@

Tsulaia, Vakhtang$^{45}$;
Tunnell, Christopher$^{79}$;

@@

Vallecorsa, Sofia$^{83}$;

@@

Vuosalo, Carl$^{118}$;
Vázquez Sierra, Carlos$^{55}$;

@@

Watts, Gordon T$^{109}$;

@@

Williams, Mike$^{52}$;
Winklmeier, Frank$^{57}$;

@@

Wuerthwein, Frank$^{74}$;
Wynne, Benjamin$^{82}$;

@@

Yang, Wei$^{62,p}$;

@@

\par {\footnotesize $^{27}$ Università e INFN, Ferrara, Ferrara, Italy}
\par {\footnotesize $^{28}$ INFN Sezione di Genova, Genova, Italy}
\par {\footnotesize $^{29}$ INFN Sezione di Milano-Bicocca, Milano, Italy}
\par {\footnotesize $^{30}$ INFN Sezione di Napoli, Università di Napoli, Napoli, Italy}
\par {\footnotesize $^{31}$ INFN Sezione di Pisa, Università di Pisa, Scuola Normale Superiore di Pisa, Pisa, Italy}
\par {\footnotesize $^{32}$ INFN Sezione di Padova, Università di Padova b, Padova, Italy}
\par {\footnotesize $^{33}$ INFN Sezione di Roma I, Università La Sapienza, Roma, Italy}
\par {\footnotesize $^{34}$ INFN Sezione di Trieste, Università di Trieste, Trieste, Italy}
\par {\footnotesize $^{35}$ INFN Sezione di Torino, Torino, Italy}
\par {\footnotesize $^{36}$ Université de Strasbourg, CNRS, IPHC UMR 7178, F-67000 Strasbourg, France}
\par {\footnotesize $^{37}$ Imperial College London, London, United Kingdom}
\par {\footnotesize $^{38}$ DSM/IRFU (Institut de Recherches sur les Lois Fondamentales de l’Univers), CEA Saclay (Commissariat à l’Énergie Atomique), Gif-sur-Yvette, France}
\par {\footnotesize $^{39}$ Thomas Jefferson National Accelerator Facility, Newport News, Virginia, VA, USA}
\par {\footnotesize $^{40}$ Jožef Stefan Institute, Ljubljana, Slovenia}
\par {\footnotesize $^{41}$ Karlsruhe Institute of Technology, Karlsruhe, Germany}
\par {\footnotesize $^{42}$ AGH University of Science and Technology, Faculty of Physics and Applied Computer Science, Krakow, Poland}
\par {\footnotesize $^{43}$ Kyungpook National University, Daegu, Republic of Korea}
\par {\footnotesize $^{44}$ LAL, Université Paris-Sud and CNRS/IN2P3, Orsay, France}
\par {\footnotesize $^{45}$ Lawrence Berkeley National Laboratory and University of California, Berkeley, CA, USA}
\par {\footnotesize $^{46}$ Laboratório de Instrumentação e Física Experimental de Partículas (LIP), Lisboa, Portugal}
\par {\footnotesize $^{47}$ Laboratoire Leprince-Ringuet, École Polytechnique, CNRS/IN2P3, Université Paris-Saclay, Palaiseau, France}
\par {\footnotesize $^{48}$ Fakultät für Physik, Ludwig-Maximilians-Universität München, München, Germany}
\par {\footnotesize $^{49}$ Laboratoire de Physique Corpusculaire, Clermont Université and Université Blaise Pascal and CNRS/IN2P3, Clermont-Ferrand, France}
\par {\footnotesize $^{50}$ Laboratoire de Physique Nucléaire et de Hautes Energies (LPNHE), Sorbonne Université, Université Paris Diderot, CNRS/IN2P3, Paris, France}
\par {\footnotesize $^{51}$ Laboratoire de Physique Subatomique et de Cosmologie, Université Joseph Fourier and CNRS/IN2P3 and Institut National Polytechnique de Grenoble, Grenoble, France}
\par {\footnotesize $^{52}$ Massachusetts Institute of Technology, Cambridge, MA, USA}
\par {\footnotesize $^{53}$ Max-Planck-Institut für Physik (Werner-Heisenberg-Institut), München, Germany}
\par {\footnotesize $^{54}$ Niels Bohr Institute, University of Copenhagen, Kobenhavn, Denmark}
\par {\footnotesize $^{55}$ Nikhef National Institute for Subatomic Physics, Amsterdam, Netherlands}
\par {\footnotesize $^{56}$ Department of Physics, New York University, New York, NY, USA}
\par {\footnotesize $^{57}$ Center for High Energy Physics, University of Oregon, Eugene, OR, USA}
\par {\footnotesize $^{58}$ Port d’Informació Científica (PIC), Universitat Autònoma de Barcelona (UAB), Barcelona, Spain}
\par {\footnotesize $^{59}$ High Energy Physics (IHEP), Protvino, Russia}
\par {\footnotesize $^{60}$ STFC Rutherford Appleton Laboratory, Didcot, United Kingdom}
\par {\footnotesize $^{61}$ Department of Physics, Royal Holloway University of London, Surrey, United Kingdom}
\par {\footnotesize $^{62}$ SLAC National Accelerator Laboratory, Menlo Park, CA, USA}
\par {\footnotesize $^{63}$ Simons Foundation, New York, NY, USA}
\par {\footnotesize $^{64}$ SoundCloud, Berlin, Germany}
\par {\footnotesize $^{65}$ SUBATECH, IMT Atlantique, Université de Nantes, CNRS-IN2P3, Nantes, France}
\par {\footnotesize $^{66}$ National Taiwan University, Taipei, Taiwan}
\par {\footnotesize $^{67}$ Tata Institute of Fundamental Research, Mumbai, India}
\par {\footnotesize $^{68}$ Technische Universit\"at Dortmund, Dortmund, Germany}
\par {\footnotesize $^{69}$ Department of Physics, University of Alberta, Edmonton, AB, Canada}
\par {\footnotesize $^{70}$ Department of Physics, University of Arizona, Tucson, AZ, USA}
\par {\footnotesize $^{71}$ H.H. Wills Physics Laboratory, University of Bristol, Bristol, United Kingdom}
\par {\footnotesize $^{72}$ Department of Physics, University of British Columbia, Vancouver, BC, Canada}
\par {\footnotesize $^{73}$ Department of Physics and Astronomy, University of California Irvine, Irvine, CA, USA}
\par {\footnotesize $^{74}$ University of California, San Diego, La Jolla, CA, USA}
\par {\footnotesize $^{75}$ Cavendish Laboratory, University of Cambridge, Cambridge, United Kingdom}
\par {\footnotesize $^{76}$ Physics Department, University of Cape Town, Cape Town, South Africa}
\par {\footnotesize $^{77}$ Carleton University, Ottawa, ON, Canada}
\par {\footnotesize $^{78}$ University of Illinois Urbana-Champaign, Champaign, Illinois, IL, USA}
\par {\footnotesize $^{79}$ Enrico Fermi Institute, University of Chicago, Chicago, IL, USA}
\par {\footnotesize $^{80}$ University of Cincinnati, Cincinnati, OH, USA}
\par {\footnotesize $^{81}$ Department of Physics, Duke University, Durham, NC, USA}
\par {\footnotesize $^{82}$ SUPA - School of Physics and Astronomy, University of Edinburgh, Edinburgh, United Kingdom}
\par {\footnotesize $^{83}$ Gangneung-Wonju National University, South Korea}
\par {\footnotesize $^{84}$ Section de Physique, Université de Genève, Geneva, Switzerland}
\par {\footnotesize $^{85}$ SUPA - School of Physics and Astronomy, University of Glasgow, Glasgow, United Kingdom}
\par {\footnotesize $^{86}$ Physikalisches Institut, Ruprecht-Karls-Universitat Heidelberg, Heidelberg, Germany}
\par {\footnotesize $^{87}$ Department of Physics and Astronomy, University of Kentucky, Lexington, KY, USA}
\par {\footnotesize $^{88}$ Physics Department, Lancaster University, Lancaster, United Kingdom}
\par {\footnotesize $^{89}$ Department of Physics, Jožef Stefan Institute and University of Ljubljana, Ljubljana, Slovenia}
\par {\footnotesize $^{90}$ Fysiska institutionen, Lunds Universitet, Lund, Sweden}
\par {\footnotesize $^{91}$ School of Physics and Astronomy, University of Manchester, Manchester, United Kingdom}
\par {\footnotesize $^{92}$ University of Maribor, Ljubljana, Slovenia}
\par {\footnotesize $^{93}$ Department of Physics, University of Massachusetts, Amherst, MA, USA}
\par {\footnotesize $^{94}$ Department of Physics, The University of Michigan, Ann Arbor, MI, USA}
\par {\footnotesize $^{95}$ Departamento de Física, Universidade do Minho, Braga, Portugal}
\par {\footnotesize $^{96}$ University of Nebraska-Lincoln, Lincoln, NE, USA}
\par {\footnotesize $^{97}$ Department of Physics and Astronomy, University of New Mexico, Albuquerque, NM, USA}
\par {\footnotesize $^{98}$ University of Notre Dame, Notre Dame, IN, USA}
\par {\footnotesize $^{99}$ Homer L. Dodge Department of Physics and Astronomy, University of Oklahoma, Norman, OK, USA}
\par {\footnotesize $^{100}$ The Ohio State University, Columbus, OH, USA}
\par {\footnotesize $^{101}$ Department of Physics, University of Oslo, Oslo, Norway}
\par {\footnotesize $^{102}$ Universidad de Oviedo, Oviedo, Spain}
\par {\footnotesize $^{103}$ Department of Physics, Oxford University, Oxford, UK}
\par {\footnotesize $^{104}$ Department of Physics and Astronomy, University of Pittsburgh, Pittsburgh, PA, USA}
\par {\footnotesize $^{105}$ Princeton University, Princeton, NJ, USA}
\par {\footnotesize $^{106}$ Rice University, Houston, TX, USA}
\par {\footnotesize $^{107}$ Universidade Estadual Paulista, São Paulo, Brazil}
\par {\footnotesize $^{108}$ Dipartimento di Fisica, Università La Sapienza, Roma, Italy}
\par {\footnotesize $^{109}$ University of Washington, Seattle, WA, USA}
\par {\footnotesize $^{110}$ School of Physics, Shandong University, Shandong, China}
\par {\footnotesize $^{111}$ Department of Physics and Astronomy, University of Sheffield, Sheffield, United Kingdom}
\par {\footnotesize $^{112}$ University of Sofia, Sofia, Bulgaria}
\par {\footnotesize $^{113}$ Department of Physics, The University of Texas at Arlington, Arlington, TX, USA}
\par {\footnotesize $^{114}$ National Research Tomsk Polytechnic University, Tomsk, Russia}
\par {\footnotesize $^{115}$ Department of Physics, University of Toronto, Toronto, ON, Canada}

>>>>

Albrecht, Johannes$^{69}$;
Alves Jr, Antonio Augusto$^{81}$;

@@

Andronico, Giuseppe$^{27}$;
Anh-Ky, Nguyen$^{122}$;
Aphecetche, Laurent$^{66}$;

@@

Asai, Makoto$^{63,p}$;

@@

Bagliesi, Giuseppe$^{32}$;

@@

Bauerdick, Lothar A.T.$^{16,c}$;
Belforte, Stefano$^{35}$;
Benjamin, Douglas$^{82}$;
Bernius, Catrin$^{63}$;
Bhimji, Wahid$^{46}$;
Bianchi, Riccardo Maria$^{105}$;

@@

Biscarat, Catherine$^{52}$;

@@

Bloom, Kenneth$^{97}$;
Boccali, Tommaso$^{32}$;
Bockelman, Brian$^{97}$;
Bold, Tomasz$^{43}$;

@@

Boveia, Antonio$^{101}$;
Bozzi, Concezio$^{28}$;
Bracko, Marko$^{93,41}$;
Britton, David$^{86}$;
Buckley, Andy$^{86}$;

@@

Calafiura, Paolo$^{46}$;

@@

Carlino, Gianpaolo$^{31}$;
Castro, Nuno$^{47,96,d}$;

@@

Chang, Philip$^{75}$;
Chapman, John$^{76}$;

@@

Clarke, Peter$^{83}$;

@@

Cogneras, Eric$^{50}$;
Coles, Jeremy$^{76}$;
Collier, Ian$^{61}$;
Colling, David$^{38}$;

@@

Costanzo, Davide$^{112}$;

@@

Cranmer, Kyle$^{57}$;

@@

Crooks, David$^{86}$;
Crépé-Renaudin, Sabine$^{52}$;
Currie, Robert$^{83}$;

@@

De, Kaushik$^{114}$;
De Cian, Michel$^{87}$;

@@

Derue, Frédéric$^{51}$;

@@

Di Guida, Salvatore$^{30}$;

@@

Doglioni, Caterina$^{91,h}$;
Dotti, Andrea$^{63,p}$;

@@

Duflot, Laurent$^{45}$;

@@

Egede, Ulrik$^{38}$;
Elmer, Peter$^{106,a}$;

@@

Farrell, Steven$^{46}$;
Ferber, Torben$^{73}$;
Filipcic, Andrej$^{41}$;
Fisk, Ian$^{64}$;

@@

Flix, José$^{59,7,g}$;
Formica, Andrea$^{39}$;
Forti, Alessandra$^{92}$;

@@

Frost, James$^{104}$;

@@

Gardner, Robert$^{80}$;
Garonne, Vincent$^{102}$;

@@

George, Simon$^{62}$;
Geurts, Frank$^{107}$;

@@

Giagu, Stefano$^{109,34}$;
Giffels, Manuel$^{42}$;
Gingrich, Douglas$^{70}$;

@@

Gligorov, Vladimir V.$^{51,b}$;
Glushkov, Ivan$^{114}$;
Gohn, Wesley$^{88}$;

@@

González Caballero, Isidro$^{103}$;
González Fernández, Juan R.$^{103}$;

@@

Grasland, Hadrien$^{45}$;
Gray, Heather$^{46}$;
Grillo, Lucia$^{92}$;
Guan, Wen$^{119}$;

@@

Gyurjyan, Vardan$^{40}$;
Hanushevsky, Andrew$^{63,p}$;

@@

Hauth, Thomas$^{42}$;

@@

Heinrich, Lukas$^{57}$;
Heiss, Andreas$^{42}$;

@@

Hildreth, Michael$^{99,f}$;
Hodgkinson, Mark$^{112}$;
Hoeche, Stefan$^{63,p}$;

@@

Huang, Xingtao$^{111}$;
Ivanchenko, Vladimir N.$^{5,115}$;
Ivanov, Todor$^{113}$;

@@

Jashal, Brij$^{68}$;

@@

Jones, Roger$^{89,a}$;
Jouvin, Michel$^{45,a}$;

@@

Kagan, Michael$^{63,p}$;
Kalderon, Charles William$^{91}$;
Kane, Meghan$^{65}$;

@@

Katz, Daniel S.$^{79}$;

@@

Kersevan, Borut Paul$^{90}$;

@@

Klute, Markus$^{94}$;
Komarov, Ilya$^{35,n}$;
Konstantinov, Dmitri$^{60}$;
Koppenburg, Patrick$^{56}$;

@@

Kreczko, Luke$^{72}$;
Kuhr, Thomas$^{49,a}$;

@@

Lampl, Walter$^{71}$;

@@

Lange, David$^{106,a}$;

@@

Leggett, Charles$^{46}$;
Letts, James$^{75}$;

@@

Li, Teng$^{83}$;

@@

Linacre, Jacob$^{61,m}$;

@@

Love, Peter$^{89}$;

@@

Magini, Nicolò$^{29}$;
Marshall, Zachary L.$^{46}$;

@@

Martin-Haugh, Stewart$^{61}$;

@@

Mazumdar, Kajari$^{68}$;
McCauley, Thomas$^{99}$;

@@

McKee, Shawn$^{95,l}$;
McNab, Andrew$^{92}$;
Mehdiyev, Rashid$^{78}$;

@@

Menasce, Dario$^{30,a}$;

@@

Mete, Alaettin Serhan$^{74}$;
Michelotto, Michele$^{33}$;
Mitrevski, Jovan$^{49}$;

@@

Morgan, Ben$^{118}$;
Mount, Richard$^{63,p}$;
Moyse, Edward$^{94}$;
Murray, Sean$^{77,10}$;

@@

Neubauer, Mark S.$^{79,a,k}$;

@@

Novaes, Sérgio$^{108}$;

@@

Ozturk, Nurcan$^{114}$;
Pacheco Pages, Andres$^{59,20,j}$;
Paganini, Michela$^{120}$;
Pansanel, Jerome$^{37}$;
Pascuzzi, Vincent R.$^{116}$;
Patrick, Glenn$^{61}$;

@@

Pearson, Ben$^{54}$;

@@

Perez-Calero Yzquierdo, Antonio$^{59,7,g}$;

@@

Petersen, Troels$^{55}$;

@@

Petzold, Andreas$^{42}$;

@@

Piilonen, Leo$^{123,i}$;

@@

Pivarski, Jim$^{106}$;

@@

Polci, Francesco$^{51}$;

@@

Puig Navarro, Albert$^{121}$;
Quast, Günter$^{42}$;
Raven, Gerhard$^{56,124}$;

@@

Ritter, Martin$^{49}$;

@@

Rodrigues, Eduardo$^{81,a,e}$;

@@

Rousseau, David$^{45}$;
Roy, Gareth$^{86}$;
Rybkine, Grigori$^{45}$;

@@

Sakuma, Tai$^{72}$;

@@

Sartirana, Andrea$^{48}$;
Schellman, Heidi$^{58}$;

@@

Schramm, Steven$^{85}$;

@@

Seidel, Sally$^{98}$;
Sekmen, Sezen$^{44}$;
Serfon, Cedric$^{102}$;
Severini, Horst$^{100}$;

@@

Seymour, Michael$^{92}$;

@@

Shapoval, Illya$^{46}$;

@@

Shiu, Jing-Ge$^{67}$;

@@

Skipsey, Sam$^{86}$;

@@

Sokoloff, Michael D.$^{81,a}$;

@@

Stark, Giordon$^{80}$;
Stewart, Gordon$^{86}$;
Stewart, Graeme A.$^{5,a}$;
Sánchez, Arturo$^{117,19}$;

@@

Taffard, Anyes$^{74}$;
Tamponi, Umberto$^{36}$;
Templon, Jeff$^{56}$;

@@

Tsulaia, Vakhtang$^{46}$;
Tunnell, Christopher$^{80}$;

@@

Vallecorsa, Sofia$^{84}$;

@@

Vuosalo, Carl$^{119}$;
Vázquez Sierra, Carlos$^{56}$;

@@

Watts, Gordon T.$^{110}$;

@@

Williams, Mike$^{53}$;
Winklmeier, Frank$^{58}$;

@@

Wuerthwein, Frank$^{75}$;
Wynne, Benjamin$^{83}$;

@@

Yang, Wei$^{63,p}$;

@@

\par {\footnotesize $^{27}$ INFN Sezione di Catania, Università di Catania, Catania, Italy}
\par {\footnotesize $^{28}$ Università e INFN, Ferrara, Ferrara, Italy}
\par {\footnotesize $^{29}$ INFN Sezione di Genova, Genova, Italy}
\par {\footnotesize $^{30}$ INFN Sezione di Milano-Bicocca, Milano, Italy}
\par {\footnotesize $^{31}$ INFN Sezione di Napoli, Università di Napoli, Napoli, Italy}
\par {\footnotesize $^{32}$ INFN Sezione di Pisa, Università di Pisa, Scuola Normale Superiore di Pisa, Pisa, Italy}
\par {\footnotesize $^{33}$ INFN Sezione di Padova, Università di Padova b, Padova, Italy}
\par {\footnotesize $^{34}$ INFN Sezione di Roma I, Università La Sapienza, Roma, Italy}
\par {\footnotesize $^{35}$ INFN Sezione di Trieste, Università di Trieste, Trieste, Italy}
\par {\footnotesize $^{36}$ INFN Sezione di Torino, Torino, Italy}
\par {\footnotesize $^{37}$ Université de Strasbourg, CNRS, IPHC UMR 7178, F-67000 Strasbourg, France}
\par {\footnotesize $^{38}$ Imperial College London, London, United Kingdom}
\par {\footnotesize $^{39}$ DSM/IRFU (Institut de Recherches sur les Lois Fondamentales de l’Univers), CEA Saclay (Commissariat à l’Énergie Atomique), Gif-sur-Yvette, France}
\par {\footnotesize $^{40}$ Thomas Jefferson National Accelerator Facility, Newport News, Virginia, VA, USA}
\par {\footnotesize $^{41}$ Jožef Stefan Institute, Ljubljana, Slovenia}
\par {\footnotesize $^{42}$ Karlsruhe Institute of Technology, Karlsruhe, Germany}
\par {\footnotesize $^{43}$ AGH University of Science and Technology, Faculty of Physics and Applied Computer Science, Krakow, Poland}
\par {\footnotesize $^{44}$ Kyungpook National University, Daegu, Republic of Korea}
\par {\footnotesize $^{45}$ LAL, Université Paris-Sud and CNRS/IN2P3, Orsay, France}
\par {\footnotesize $^{46}$ Lawrence Berkeley National Laboratory and University of California, Berkeley, CA, USA}
\par {\footnotesize $^{47}$ Laboratório de Instrumentação e Física Experimental de Partículas (LIP), Lisboa, Portugal}
\par {\footnotesize $^{48}$ Laboratoire Leprince-Ringuet, École Polytechnique, CNRS/IN2P3, Université Paris-Saclay, Palaiseau, France}
\par {\footnotesize $^{49}$ Fakultät für Physik, Ludwig-Maximilians-Universität München, München, Germany}
\par {\footnotesize $^{50}$ Laboratoire de Physique Corpusculaire, Clermont Université and Université Blaise Pascal and CNRS/IN2P3, Clermont-Ferrand, France}
\par {\footnotesize $^{51}$ Laboratoire de Physique Nucléaire et de Hautes Energies (LPNHE), Sorbonne Université, Université Paris Diderot, CNRS/IN2P3, Paris, France}
\par {\footnotesize $^{52}$ Laboratoire de Physique Subatomique et de Cosmologie, Université Joseph Fourier and CNRS/IN2P3 and Institut National Polytechnique de Grenoble, Grenoble, France}
\par {\footnotesize $^{53}$ Massachusetts Institute of Technology, Cambridge, MA, USA}
\par {\footnotesize $^{54}$ Max-Planck-Institut für Physik (Werner-Heisenberg-Institut), München, Germany}
\par {\footnotesize $^{55}$ Niels Bohr Institute, University of Copenhagen, Kobenhavn, Denmark}
\par {\footnotesize $^{56}$ Nikhef National Institute for Subatomic Physics, Amsterdam, Netherlands}
\par {\footnotesize $^{57}$ Department of Physics, New York University, New York, NY, USA}
\par {\footnotesize $^{58}$ Center for High Energy Physics, University of Oregon, Eugene, OR, USA}
\par {\footnotesize $^{59}$ Port d’Informació Científica (PIC), Universitat Autònoma de Barcelona (UAB), Barcelona, Spain}
\par {\footnotesize $^{60}$ High Energy Physics (IHEP), Protvino, Russia}
\par {\footnotesize $^{61}$ STFC Rutherford Appleton Laboratory, Didcot, United Kingdom}
\par {\footnotesize $^{62}$ Department of Physics, Royal Holloway University of London, Surrey, United Kingdom}
\par {\footnotesize $^{63}$ SLAC National Accelerator Laboratory, Menlo Park, CA, USA}
\par {\footnotesize $^{64}$ Simons Foundation, New York, NY, USA}
\par {\footnotesize $^{65}$ SoundCloud, Berlin, Germany}
\par {\footnotesize $^{66}$ SUBATECH, IMT Atlantique, Université de Nantes, CNRS-IN2P3, Nantes, France}
\par {\footnotesize $^{67}$ National Taiwan University, Taipei, Taiwan}
\par {\footnotesize $^{68}$ Tata Institute of Fundamental Research, Mumbai, India}
\par {\footnotesize $^{69}$ Technische Universit\"at Dortmund, Dortmund, Germany}
\par {\footnotesize $^{70}$ Department of Physics, University of Alberta, Edmonton, AB, Canada}
\par {\footnotesize $^{71}$ Department of Physics, University of Arizona, Tucson, AZ, USA}
\par {\footnotesize $^{72}$ H.H. Wills Physics Laboratory, University of Bristol, Bristol, United Kingdom}
\par {\footnotesize $^{73}$ Department of Physics, University of British Columbia, Vancouver, BC, Canada}
\par {\footnotesize $^{74}$ Department of Physics and Astronomy, University of California Irvine, Irvine, CA, USA}
\par {\footnotesize $^{75}$ University of California, San Diego, La Jolla, CA, USA}
\par {\footnotesize $^{76}$ Cavendish Laboratory, University of Cambridge, Cambridge, United Kingdom}
\par {\footnotesize $^{77}$ Physics Department, University of Cape Town, Cape Town, South Africa}
\par {\footnotesize $^{78}$ Carleton University, Ottawa, ON, Canada}
\par {\footnotesize $^{79}$ University of Illinois Urbana-Champaign, Champaign, Illinois, IL, USA}
\par {\footnotesize $^{80}$ Enrico Fermi Institute, University of Chicago, Chicago, IL, USA}
\par {\footnotesize $^{81}$ University of Cincinnati, Cincinnati, OH, USA}
\par {\footnotesize $^{82}$ Department of Physics, Duke University, Durham, NC, USA}
\par {\footnotesize $^{83}$ SUPA - School of Physics and Astronomy, University of Edinburgh, Edinburgh, United Kingdom}
\par {\footnotesize $^{84}$ Gangneung-Wonju National University, South Korea}
\par {\footnotesize $^{85}$ Section de Physique, Université de Genève, Geneva, Switzerland}
\par {\footnotesize $^{86}$ SUPA - School of Physics and Astronomy, University of Glasgow, Glasgow, United Kingdom}
\par {\footnotesize $^{87}$ Physikalisches Institut, Ruprecht-Karls-Universitat Heidelberg, Heidelberg, Germany}
\par {\footnotesize $^{88}$ Department of Physics and Astronomy, University of Kentucky, Lexington, KY, USA}
\par {\footnotesize $^{89}$ Physics Department, Lancaster University, Lancaster, United Kingdom}
\par {\footnotesize $^{90}$ Department of Physics, Jožef Stefan Institute and University of Ljubljana, Ljubljana, Slovenia}
\par {\footnotesize $^{91}$ Fysiska institutionen, Lunds Universitet, Lund, Sweden}
\par {\footnotesize $^{92}$ School of Physics and Astronomy, University of Manchester, Manchester, United Kingdom}
\par {\footnotesize $^{93}$ University of Maribor, Ljubljana, Slovenia}
\par {\footnotesize $^{94}$ Department of Physics, University of Massachusetts, Amherst, MA, USA}
\par {\footnotesize $^{95}$ Department of Physics, The University of Michigan, Ann Arbor, MI, USA}
\par {\footnotesize $^{96}$ Departamento de Física, Universidade do Minho, Braga, Portugal}
\par {\footnotesize $^{97}$ University of Nebraska-Lincoln, Lincoln, NE, USA}
\par {\footnotesize $^{98}$ Department of Physics and Astronomy, University of New Mexico, Albuquerque, NM, USA}
\par {\footnotesize $^{99}$ University of Notre Dame, Notre Dame, IN, USA}
\par {\footnotesize $^{100}$ Homer L. Dodge Department of Physics and Astronomy, University of Oklahoma, Norman, OK, USA}
\par {\footnotesize $^{101}$ The Ohio State University, Columbus, OH, USA}
\par {\footnotesize $^{102}$ Department of Physics, University of Oslo, Oslo, Norway}
\par {\footnotesize $^{103}$ Universidad de Oviedo, Oviedo, Spain}
\par {\footnotesize $^{104}$ Department of Physics, Oxford University, Oxford, UK}
\par {\footnotesize $^{105}$ Department of Physics and Astronomy, University of Pittsburgh, Pittsburgh, PA, USA}
\par {\footnotesize $^{106}$ Princeton University, Princeton, NJ, USA}
\par {\footnotesize $^{107}$ Rice University, Houston, TX, USA}
\par {\footnotesize $^{108}$ Universidade Estadual Paulista, São Paulo, Brazil}
\par {\footnotesize $^{109}$ Dipartimento di Fisica, Università La Sapienza, Roma, Italy}
\par {\footnotesize $^{110}$ University of Washington, Seattle, WA, USA}
\par {\footnotesize $^{111}$ School of Physics, Shandong University, Shandong, China}
\par {\footnotesize $^{112}$ Department of Physics and Astronomy, University of Sheffield, Sheffield, United Kingdom}
\par {\footnotesize $^{113}$ University of Sofia, Sofia, Bulgaria}
\par {\footnotesize $^{114}$ Department of Physics, The University of Texas at Arlington, Arlington, TX, USA}
\par {\footnotesize $^{115}$ National Research Tomsk Polytechnic University, Tomsk, Russia}
